Wissenschaftliches Arbeiten

### 2014-06-29 paper.tex
Explaining what n is in the context of complete enumeration as solution strategy of comb. auctions
Correcting wrong reference

\cite[Chapter~2]{San02} lists some possible algorithms for solving that problem. The first proposed technique is an enumeration of all possible exhaustive partitions of the available items but that solution does not scale beyond a hand full of goods. Its upper limit is $\mathcal O(n^n)$. Another exact solution which performs much better is the use of dynamic programming for which \cite[Chapter~2.2]{San02} provides an algorithm with $\mathcal O(3^n)$.

@@

\subsection{Transportation Market}
\cite{CELM07}~had a look at the American truckload transportation market during the late 1990s and early 2000s. In this business more and more combinatorial auctions are used to cut drives without load and increase competitiveness.

>>>>

\cite[Chapter~2]{San02} lists some possible algorithms for solving that problem. The first proposed technique is an enumeration of all possible exhaustive partitions of the available items but that solution does not scale beyond a hand full of goods. Its upper limit is $\mathcal O(n^n)$, with $n$ being the amount of auctioned goods. Another exact solution which performs much better is the use of dynamic programming for which \cite[Chapter~2.2]{San02} provides an algorithm with $\mathcal O(3^n)$.

@@

\subsection{Transportation Market}
\cite{CS06}~had a look at the American truckload transportation market during the late 1990s and early 2000s. In this business more and more combinatorial auctions are used to cut drives without load and increase competitiveness.
